Adapting Duplicate Filters to a Sliding Window Context

### 2020-03-20 qhtv2.tex
Merging

\subsection{DDF Comparison}
A filter comparison was already made in \cite{10.1145/3297280.3297335}. Taking the same filters parameters, created another benchmark, studying the resistance of each DDF to saturation. We added the lower bound on the error rate. More details about the experiments are given in Section~\ref{sub:saturation}. We observe in Figure~\ref{fig:graph_n} that the most efficient DDF is the QHT \cite{10.1145/3297280.3297335}.

%However, as noted in Section~\ref{sub:related}, A2 filters can be considered as a queuing filter, with $L=2$ and Bloom filters as subfilters. Hence, as it is not interesting to put a queueing filter inside a queueing filter, we will rather use QHT for practical benchmarking of the queueing filter.

@@

%In the experiments we use QHT for practical benchmarking of the queueing filter.

>>>>

@@

In the experiments we use QHT for the benchmarking of the queueing construction.
